\section{Evaluation Plan}
\label{sec:evaluation_plan}

\begin{enumerate}
\item \textbf{Task-2} Usual call center evaluation metrics like length of call etc. Also, may be number of repeated instructions will serve as a good evaluation metric. For example, if the scammer repeats: ``hey, do this!'' - that's bad. We can supplement these with Qualitative feedback from the scam-baiter community who can also comment on how to improve our product. Their domain expertise will help us as well.
[TODO]: Also see how chatbots get evaluated and see if they can be incorporated.

Another evaluation metric is simply how many milestone points we have reached. Task-2 will involve qualitative analysis of scam transcripts. 

Furhter, with Task-2 (see Bhuepndra's reviews) some scammers might find out that we are faking -- as determined by the length of the call mentioned above. 



\end{enumerate}

% Also discuss risks here.
\section{Discussion}
\label{sec:discussion}

\textbf{Limitations regarding the comprehensiveness of the topics we will focus on.} We make no claim that the topics we focus on represent the complete spectrum of human-in-the-loop social engineering attacks. THe topics of our focus will largely be driven by the topics However, FBI complaint reports state that tech support scams and cryptocurrency scams will represent a large total. Further, we expect the engineering tools for all the three thrusts will be easily repurposable to scams that continue to evolve. 


\textbf{Risk mitigation}

Because of the highly integrated and sequential structure of the proposal, it is important to highlight potential risks for the proposal pipeline.

\begin{enumerate}
    \item \textbf{Task-1:} While we already have letter of support from the community and expression of interest from community members, it is feasible that either we might not get all interest, or the scam baiting responses are not representative. In these cases, we will supplement with passive data.
    \item \textbf{Task-2:} If Task-2 fails, then, Task-3 and Education plan get affected. However, we can pursue manual data collection (even integrate it with older adults to pursue alternate active education) and since numbers (cite) show that only small is enough - this will be good for us.
\end{enumerate}

%\subsection{Risks to the Project}

